Laplacian envelope

### 2022-12-08 Notes/laplace.tex
uni eigenmode and heuristic env

The first of these equations is solved by
%
\begin{equation}\label{eq:detagensol}
  \delta\etwm_i = B\e^{\beta(i-1)} + C\e^{\beta(1-i)},
  \qquad\text{where}\qquad
  s = S(\beta) \equiv 2 \sinh^2 \prn{\frac{\beta}{2}}
    = \cosh (\beta) - 1,
\end{equation}
%
with \(B\) and \(C\) determined by the boundary conditions provided by the last two equations of \eqref{eq:detahalf}:
%
\begin{equation}\label{eq:unicoeffs}
  B = -\frac{1}{s(1 + \e^{-\beta}) \cosh \prn{m \beta}},
  \qquad
  C = -\frac{1}{s(\e^{\beta} + 1) \cosh \prn{m \beta}}.
\end{equation}
%
This can be used to compute the Laplace transform
%
\begin{equation}\label{eq:unilaplace}
  A(s) = \frac{\etwm_1(s)}{m}
   = \frac{1}{m}\prn{\frac{1}{s}+B+C}
   = \frac{2\sinh^2\prn{\frac{m \beta}{2}}}{m s \cosh\prn{m \beta}}
   = \frac{2 S\prn{m \beta}}{M s \prn{S\prn{m \beta} + 1}}.
\end{equation}
%
This has poles as \( \beta = \frac{(2n-1)\pi\ir}{2m} \), therefore
%
\begin{equation}\label{eq:unieig}
  q_n = 1 - \cos\frac{(2n-1)\pi}{2m} = 2 \sin^2\frac{(2n-1)\pi}{4m},
  \qquad
  \CI_n = \frac{(-1)^{n-1} \sin\frac{(2n-1)\pi}{2m}}{m^2 q_n},
  \qquad n = 1,\dots,m.
\end{equation}
%
Note that these are only the eigenmodes with nonzero \(\CI_n\).

In reality, \(M\) can only take even integer values.
However, one can find a heuristic approximation to the envelope by maximising \wrt \(M\).
We find that
%
\begin{multline}\label{eq:unienv}
  M_* = \pm\frac{2y_*}{\beta},
  \quad
  s = 2\sinh^2\frac{y_*}{M_*},
  \qquad
  \hat{A}_*(s) = \prn{\frac{ \sinh y_* }{ \cosh^2 y_* }} 
      \frac{\abs{\beta(s)}}{s},
  \\ \text{where}\quad
  y_* = \tanh \frac{y_*}{2} \cosh y_* \approx 1.50553,
  \qquad
\end{multline}
%
and \(\beta(s)\) is given by the second formula of \cref{eq:detagensol}.

@@

We will phrase it in terms of \(\snrb(\tau)\), reintroducing \(r\):
%
\begin{equation}\label{eq:envunits}
  \snrb(\tau) = \frac{ \sqrt{N} \hat{A}\prn{\frac{1}{r\tau}} }{ r\tau },
  \qquad
  \beta(\tau) = \sinh\inv \!\!\sqrt{1/2r\tau}.
\end{equation}
%
Then, combining \cref{eq:binaryenv,eq:unienv,eq:stickylaplace}, 
% using the notation \( \Delta_{\varepsilon}[T(M)] = T(M) - \varepsilon T(M-2) \) for any function \(T(M)\), 
we find
%
\begin{equation}\label{eq:henv}
  \snrb(\tau) = \left\{
\begin{aligned}
  & \frac{\sqrt{N}}{1+r\tau}, &
  & r\tau \leq \tfrac{1}{2\sinh^2\frac{y_*}{2}} , \\
  & \sqrt{N} \prn{\frac{ \sinh y_* }{ \cosh^2 y_* }} \beta(\tau), &
  \tfrac{1}{2\sinh^2 \frac{y_*}{2}} \leq & r\tau \leq \tfrac{1}{2\sinh^2 \frac{y_*}{M}} , \\
  & \frac{\sqrt{N}\brk{S\prn{\tfrac{M\beta}{2}} - S\prn{\tfrac{(M-2)\beta}{2}}}}
        {\brk{\sqrt{{\frac{M-2}{2} S\prn{\tfrac{M\beta}{2}} - \frac{M}{2} S\prn{\tfrac{(M-2)\beta}{2}}}} + 1}^2} , &
  % & \max_{\varepsilon \in [0,1]} \brc{
  %     \frac{2\sqrt{N}(1-\varepsilon) \Delta_{\varepsilon}\brk{S\prn{\tfrac{M\beta}{2}}}}
  %     {\Delta_{\varepsilon}\brk{M} \Delta_{\varepsilon}\brk{S\prn{\tfrac{M\beta}{2}} + 1} } 
  %     }, &
  \tfrac{1}{2\sinh^2 \frac{y_*}{M}} \leq & r\tau ,
\end{aligned}
\right.
\end{equation}
%
where \(S(\beta) = \cosh \beta(\tau) - 1\) (see \cref{eq:detagensol}) and \(y_*\) is defined in \cref{eq:unienv}.

>>>>

The first of these equations is solved by
%
\begin{equation}\label{eq:detagensol}
  \delta\etwm_i = B\e^{\beta(i-1)} + C\e^{\beta(1-i)},
  \qquad\text{where}\qquad
  s = S(\beta) \equiv 2 \sinh^2 \prn{\frac{\beta}{2}}
    = \cosh (\beta) - 1,
\end{equation}
%
with \(B\) and \(C\) determined by the boundary conditions provided by the last two equations of \eqref{eq:detahalf}:
%
\begin{equation}\label{eq:unicoeffs}
  B = -\frac{1}{s(1 + \e^{-\beta}) \cosh \prn{m \beta}},
  \qquad
  C = -\frac{1}{s(\e^{\beta} + 1) \cosh \prn{m \beta}}.
\end{equation}
%
This can be used to compute the Laplace transform
%
\begin{equation}\label{eq:unilaplace}
  A(s) = \frac{\etwm_1(s)}{m}
   = \frac{1}{m}\prn{\frac{1}{s}+B+C}
   = \frac{2\sinh^2\prn{\frac{m \beta}{2}}}{m s \cosh\prn{m \beta}}
   = \frac{2 S\prn{m \beta}}{M s \prn{S\prn{m \beta} + 1}}.
\end{equation}
%
This has poles as \( \beta = \frac{(2n-1)\pi\ir}{2m} \).
From \cref{eq:laplaceeig} we see that the poles and residues in the \(s\)-plane are \( (-q_n, \CI_n) \), therefore:
%
\begin{equation}\label{eq:unieig}
  q_n = 1 - \cos \brkfrac{(2n-1)\pi}{2m} 
      % = 2 \sin^2\frac{(2n-1)\pi}{4m},
  \qquad
  \CI_n = \frac{(-1)^{n-1}}{m^2} \cot \brkfrac{(2n-1)\pi}{4m},
  \qquad n = 1,\dots,m.
\end{equation}
%
Note that these are only the eigenmodes with nonzero \(\CI_n\).

In reality, \(M\) can only take even integer values.
However, one can find a heuristic approximation to the envelope by maximising \wrt \(M\).
We find that
%
\begin{multline}\label{eq:unienv}
  M_* = \pm\frac{2y_*}{\beta},
  \quad
  s = 2\sinh^2\frac{y_*}{M_*},
  \qquad
  \hat{A}_*(s) = \prn{\frac{ \sinh y_* }{ \cosh^2 y_* }} 
      \frac{\operatorname{arccosh}(1+s)}{s},
  \\ \text{where}\quad
  y_* = \tanh \frac{y_*}{2} \cosh y_* \approx 1.50553.
\end{multline}
%
% and \(\beta(s)\) is given by the second formula of \cref{eq:detagensol}.

@@

We will phrase it in terms of \(\snrb(\tau)\), reintroducing \(r\):
%
\begin{equation}\label{eq:envunits}
  \snrb(\tau) = \frac{ \sqrt{N} \hat{A}\prn{\frac{1}{r\tau}} }{ r\tau },
  \qquad
  \beta(\tau) = \sinh\inv \!\!\sqrt{1/2r\tau}.
\end{equation}
%
Then, combining \cref{eq:binaryenv,eq:unienv,eq:stickylaplace}, 
% using the notation \( \Delta_{\varepsilon}[T(M)] = T(M) - \varepsilon T(M-2) \) for any function \(T(M)\), 
we find
%
\begin{equation}\label{eq:henv}
  \snrb(\tau) = \left\{
\begin{aligned}
  & \frac{\sqrt{N}}{1+r\tau}, &
  & r\tau \leq \tfrac{1}{2\sinh^2\frac{y_*}{2}} , \\
  & \sqrt{N} \prn{\frac{ \sinh y_* }{ \cosh^2 y_* }} \beta(\tau), &
  \tfrac{1}{2\sinh^2 \frac{y_*}{2}} \leq & r\tau \leq \tfrac{1}{2\sinh^2 \frac{y_*}{M}} , \\
  & \frac{\sqrt{N}\brk{S\prn{\tfrac{M\beta(\tau)}{2}} - S\prn{\tfrac{(M-2)\beta(\tau)}{2}}}}
        {\brk{\sqrt{{\frac{M-2}{2} S\prn{\tfrac{M\beta(\tau)}{2}} - \frac{M}{2} S\prn{\tfrac{(M-2)\beta(\tau)}{2}}}} + 1}^2} , &
  % & \max_{\varepsilon \in [0,1]} \brc{
  %     \frac{2\sqrt{N}(1-\varepsilon) \Delta_{\varepsilon}\brk{S\prn{\tfrac{M\beta}{2}}}}
  %     {\Delta_{\varepsilon}\brk{M} \Delta_{\varepsilon}\brk{S\prn{\tfrac{M\beta}{2}} + 1} } 
  %     }, &
  \tfrac{1}{2\sinh^2 \frac{y_*}{M}} \leq & r\tau ,
\end{aligned}
\right.
\end{equation}
%
where \(S(\beta) = \cosh \beta - 1\), \( S(\beta(\tau)) = 1/\tau \) (see \cref{eq:detagensol}) and \(y_*\) is defined in \cref{eq:unienv}.
